Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-04-11 presentation/presentation.tex
Added blank slides
added engine models stuff to the presentation
Updated questions slide
moved some figures around

\begin{frame}{Motivation and Background}
	\begin{center}
	Currently available multirotor capabilities
	\end{center}
	\begin{figure}
		\begin{center}
			\includegraphics[width=.70\textwidth]{current_capabilities.png}
			\label{current_capabilities}
		\end{center}
	\end{figure}
\end{frame}

\begin{frame}{Models}
	\begin{itemize}
		\item{To represent the aerodynamics of each rotor, we used Combined Differential Blade Element and Momentum Theory for nonuniform inflow.}
		\begin{center}
		$ dT = \frac{1}{2} \rho a \Omega^2 r^2 (\theta - \phi) c \  dr $

		$ dQ = \frac{1}{2} \rho \Omega^2 r^3 c (\delta + \phi C_L) \ dr $
		\end{center}
	\end{itemize}

@@

\begin{frame}{Optimization Method}

>>>>

\begin{frame}{Introduction}

	What is a gas quad...
\end{frame}

\begin{frame}{Motivation and Background}
	\begin{center}
	Currently available multirotor capabilities
	\end{center}
	\begin{figure}
		\begin{center}
			\includegraphics[width=.70\textwidth]{../current_capabilities.png}
			\label{current_capabilities}
		\end{center}
	\end{figure}
\end{frame}

\begin{frame}{Engine Models}

	\begin{figure}
		\begin{center}
			\includegraphics[width=.70\textwidth]{../mass.png}
			\label{fig:eng_mass}
		\end{center}
	\end{figure}
\end{frame}

\begin{frame}{Engine Models}	
	\begin{figure}
		\begin{center}
			\includegraphics[width=.70\textwidth]{../max_power.png}
			\label{fig:eng_power}
		\end{center}
	\end{figure}

@@

\begin{frame}{Models}
	\begin{itemize}
		\item{To represent the aerodynamics of each rotor, we used Combined Differential Blade Element and Momentum Theory for nonuniform inflow.}
		\begin{center}
		$$ dT = \frac{1}{2} \rho a \Omega^2 r^2 (\theta - \phi) c \  dr $$
		$$ dQ = \frac{1}{2} \rho \Omega^2 r^3 c (\delta + \phi C_L) \ dr $$
		\end{center}
	\end{itemize}

\begin{frame}{Optimization Method}
	Design Variables
	\begin{itemize}
		\item{Engine Size}
		\item{Rotor Size}
		\item{Fuel Capacity}
		\item{Fuel Burn Rate}
		\item{theta hover}
		\item{omega}
	\end{itemize}

	Flight Time = f(Fuel Capacity/Fuel Rate)

	C = ...

	SNOPT
\end{frame}

\begin{frame}{Results}
	\begin{figure}
		\begin{center}
			\includegraphics[width=.70\textwidth]{../pareto_front.png}
			\label{fig:pareto}
		\end{center}
	\end{figure}
\end{frame}

\begin{frame}{Results}
	\begin{figure}
		\begin{center}
			\includegraphics[width=.70\textwidth]{../engine_size_vs_payload.png}
			\label{fig:pareto}
		\end{center}
	\end{figure}
\end{frame}

\begin{frame}{Lessons Learned}
	\begin{itemize}
		\item{Helicopter rotor dynamics are difficult to conceptualize and calculate.}
		\item{Over-simplification of aerodynamic model leads to unrealistic results.}
		\item{large, slow props - https://youtu.be/syJq10EQkog?t=7s}

	\end{itemize}
\end{frame}

\begin{frame}{Questions}

		\begin{center}
			Questions?
		\end{center}
